DESIGNATION_DRAFT

### 2021-06-18 R/DESIGNATION_DRAFT.Rmd
.ONFGuyafortaxojoin

NAtable <- inventoryA[is.na(inventoryA$Commercial),] #2101 ind not linked
NAtablescfc <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$ScientificName)) #264 sp not linked
NAtablevern <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$VernName)) #122 sp not linked

NAtablevern <- unique(NAtable$VernName) #264 
NAtablescfc <- unique(NAtable$ScientificName) #122

filter(inventoryA, Commercial =="1") #177 ind
filter(inventoryA, Commercial =="2") #1267 ind
comerc <- filter(inventoryA, Commercial =="1"| Commercial =="2")
all(comerc$CommercialSp == TRUE)
```

>>>>

NAtable <- inventoryA[is.na(inventoryA$Commercial),] #2151 ind not linked
NAtablescfc <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$ScientificName)) #270 sp not linked
NAtablevern <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$VernName)) #126 sp not linked

NAtablevern <- unique(NAtable$VernName) #126 
NAtablescfc <- unique(NAtable$ScientificName) #270

filter(inventoryA, Commercial =="1") #177 ind
filter(inventoryA, Commercial =="2") #1211 ind
comerc <- filter(inventoryA, Commercial =="1"| Commercial =="2")#1388
all(comerc$CommercialSp == TRUE)#FALSE
```
